\Huge Handwritten digit recognition

### 2017-02-08 doc/Paper.tex
Paper: more visible TODOs & interactive section

\usepackage{amsmath}  % equations
\usepackage{cite}  % bibliograby
\usepackage{graphicx}  % images
\usepackage{pgfplots}  % plots
  \pgfplotsset{width=10cm,compat=1.9} % plots settings
  \usepgfplotslibrary{external}
  \tikzexternalize

@@

@@

\vspace{5cm}
\begin{abstract}
TODO: rewrite when paper is done, talk about each section

@@

\newpage
TODO: introduction?

\section{Problem statement}
\label{sec:problem}
Given a picture of a handwritten digit, label it accordingly 0 - 9.

@@

\paragraph{Prediction}
TODO

@@

TODO

@@

@@

@@

\newpage
\section{Graphical Interface}
TODO: picture of resizing

TODO: picture of GUI

@@

The most expensive matrix operations are dot products and exponentiation. For matrix multiplication, we explored the Strassen algorithm, $O(n^{2.8})$, and the Coppersmith–Winograd algorithm, $O(n^{2.37})$. Although they achieve high asymptotic performance, hidden constants make them impractical in our case. We went with the Naive, $\Theta(n^3)$, algorithm with the $ikj$ optimization.

>>>>

\usepackage{amsmath}  % equations
\usepackage{cite}  % bibliograby
\usepackage{graphicx}  % images
\usepackage{pgfplots}  % plots
  \pgfplotsset{width=10cm,compat=1.9} % plots settings
  \usepgfplotslibrary{external}
  \tikzexternalize
\usepackage{todonotes}

@@

% floor operator
\newcommand{\floor}[1]{\lfloor {#1} \rfloor}
\newcommand{\TODO}[1]{\noindent \textbf{\textcolor{red}{TODO: #1}}}

@@

\vspace{5cm}
\begin{abstract}
\TODO{rewrite when paper is done, talk about each section}

@@

\newpage
\TODO{introduction?}

\section{Problem statement}
\label{sec:problem}
Given a picture of a handwritten digit, label it accordingly 0 - 9.
\TODO{more here}

@@

\paragraph{Prediction}
\TODO{explain prediction?}

@@

\TODO{more about evaluation?}

\noindent The following chart illustrates model evolution, both on the test and on the training set, after each pass through the dataset.

@@

\TODO{comment on chart}

@@

The following chart illustrates the improvement brought by parallelization on one pass through the data:

@@

\TODO{comment on chart}

\newpage
\section{Graphical Interface}
The user is presented with a blank box in which to draw a digit to be recognized. Upon request, the prediction along with the model's confidence in it is displayed.

\missingfigure[figcolor=white]{GUI}

\noindent Since the model was trained on $28 \times 28$ images, we need to pass the input in the same format. On today's screens, an input box of $28 \times 28$ pixels would look comically small. The raw input must be resized accordingly.

The simplest down-sizing method is taking each block of pixels in the original image and averaging it to form a single pixel in the resulting image. For simplicity, we assume square images and pixels with only one channel -- grayscale. Eg: an image with $n^2$ original pixels is condensed to $s^2$ pixels, meaning a factor of $f=\frac{n}{s}$. That means each of the $s^2$ pixels is a sum of a $f \times f$ block divided by $f^2$.

The trouble appears with encoding the image -- both the raw image and the model's inputs are in array form instead of a matrix. Ie: the pixels are all placed one after another starting from the top left corner.

\missingfigure[figcolor=white]{resizing example pdf}
The transformation can be computed by \textit{compacting} the columns:
$\sum_i Orig_i$ for column at index $\floor{\frac{i}{f}}$. Then for rows: $\sum_i Col_i$ for pixel at index $(i \bmod s) + \floor{\frac{i}{s \times f}}$. Where $Orig$ denotes the the original image $Col$ the column-wise averages.

@@

The most expensive matrix operations are dot products and exponentiation. For matrix multiplication, we explored the Strassen algorithm, $O(n^{2.8})$, and the Coppersmith–Winograd algorithm, $O(n^{2.37})$. Although they achieve high asymptotic performance, hidden constants make them impractical in our case. We went with the Naive, $\Theta(n^3)$, algorithm with the $ikj$ optimization. For exponentiation, we rely on STL's implementation, although this can be further optimized.
